R Notebook

### 2025-03-16 final/final_MoritzPeistNoemiLucchiSimonVellin.Rmd
Added PostGIS performance improvement and switched to primary and secondary roads only

---
title: "R Notebook"
output: html_notebook
---

@@

```{r Packages}
library(data.table)   # For faster data manipulation
library(tidyverse)    # For data manipulation and visualization
library(sf)           # For spatial data handling
library(leaflet)      # For interactive maps
library(leaflet.extras) # For additional leaflet features
library(mapview)      # For easier map visualization
library(tmap)         # For thematic maps
library(tigris)       # For US road networks
library(future)       # For parallel processing
library(future.apply) # For parallel processing with apply functions

@@

```{r Data Load Roads}
# Get US roads (this can be slow for the entire US, so we might want to limit by state)

# First get all counties in California
ca_counties <- counties("CA", year = 2021)

# Then get roads for each county
ca_roads_list <- lapply(ca_counties$COUNTYFP, function(county_code) {
  roads("CA", county = county_code, year = 2021)
})

# Optionally combine all county road data into one object
ca_roads <- do.call(rbind, ca_roads_list)
```

```{r Static Maps}
# Static map for Accidents with year coloring
# First, store your plot in a variable
ca_plot <- ggplot() +
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  geom_sf(data = df.acc.sf %>% filter(State == "CA"), 
          aes(color = factor(year)), alpha = 0.7, size = 0.5) +
  scale_color_viridis_d(name = "Year") +  # Use viridis color palette for discrete values
  theme_minimal() +
  labs(title = "US Road Accidents by Year (2016-2021)") +
  theme(legend.position = "bottom")
print(ca_plot)
# Then save it using ggsave
#ggsave(filename = "imgs/california_accidents.png", 
#       plot = ca_plot,
#       width = 10, # width in inches
#       height = 8, # height in inches
#       dpi = 300)  # resolution

# Construction sites map with year coloring
# First, store our plot in a variable
ca_const_plot <- ggplot() +
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  geom_sf(data = df.const.sf %>% filter(State == "CA"), 
          aes(color = factor(year)), alpha = 0.7, size = 0.5) +
  scale_color_viridis_d(name = "Year") +  # Use viridis color palette for discrete values
  theme_minimal() +
  labs(title = "US Construction Sites by Year (2016-2021)") +
  theme(legend.position = "bottom")
print(ca_const_plot)
# Then save it using ggsave
#ggsave(filename = "imgs/california_construction.png", 
#       plot = ca_const_plot,
#       width = 10, # width in inches
#       height = 8, # height in inches
#       dpi = 300)  # resolution
```

@@

@@

```{r Buffer Zone Analysis}
# Set up parallel processing
future::plan(future::multisession, workers = parallel::detectCores() - 1)

# Set sf to use parallel processing
sf_use_s2(FALSE)  # Disable S2 spherical geometry
cores <- parallel::detectCores() - 1

# Process each dataset with batching
cat("Creating point buffers...\n")
const_buffers <- create_buffers_in_batches(df.const.sf, buffer_dist = 1000, batch_size = 500)

# Return to sequential processing
future::plan(future::sequential)
sf_use_s2(TRUE)  # Re-enable S2 spherical geometry

# Find accidents within construction zones
# Use a spatial index and parallel processing
plan(multisession, workers = parallel::detectCores() - 1)  # Use parallel processing

accidents_in_construction <- df.acc.sf %>%
  st_join(ca_const_buffers, join = st_within, prepared = TRUE)

# Reset to sequential processing when done
plan(sequential)

# Count accidents per construction zone
accidents_per_zone <- accidents_in_construction %>%
  group_by(ID) %>%  # Grouping by the ID column
  summarize(accident_count = n())

# Visualize construction zones with accident counts
# First, store our plot in a variable
accident_zones_plot <- ggplot() +
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  geom_sf(data = accidents_per_zone, aes(fill = accident_count), alpha = 0.7) +
  scale_fill_viridis_c() +
  theme_minimal() +
  labs(title = "Accident Counts within Construction Zones (2016-2021)")

@@

# Then save it using ggsave
#ggsave(filename = "imgs/accident_counts_construction_zones.png", 
#       plot = accident_zones_plot,
#       width = 10, # width in inches
#       height = 8, # height in inches
#       dpi = 300)  # resolution
```

Advanced construction sites:

```{r SF linestring}
# Convert construction data to linestring sf object
df.const.lines <- df.const %>%
  filter(!is.na(Start_Lat) & !is.na(Start_Lng) & !is.na(End_Lat) & !is.na(End_Lng)) %>%
  mutate(geometry = pmap(list(Start_Lng, Start_Lat, End_Lng, End_Lat), 
                         function(start_lng, start_lat, end_lng, end_lat) {
                           coords <- matrix(c(start_lng, start_lat, 
                                             end_lng, end_lat), 
                                           ncol = 2, byrow = TRUE)
                           st_linestring(coords)
                         })) %>%
  st_sf(crs = 4326)
```

```{r Maps with Construction Lines}
# Static map with construction line segments
ggplot() +
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  geom_sf(data = df.const.lines %>% filter(State == "CA"), 
          color = "orange", size = 1) +
  theme_minimal() +
  labs(title = "US Construction Segments (2016-2021)")

# Interactive map with construction segments focused on California
construction_segment_map <- leaflet() %>%
  addTiles() %>%
  addPolylines(data = df.const.lines, 
               color = "orange",
               weight = 3,
               opacity = 0.7,
               popup = ~paste("ID:", ID, "<br>Duration:", Duration)) %>%
  setView(lng = -119.4179, lat = 36.7783, zoom = 6) %>%  # Center on California
  setMaxBounds(lng1 = -124.6, lat1 = 42.0,    # Northwest corner of CA
               lng2 = -114.1, lat2 = 32.5)    # Southeast corner of CA

@@

```{r Construction Impact Analysis with Buffers}
# Set up parallel processing
future::plan(future::multisession, workers = parallel::detectCores() - 1)

# Set sf to use parallel processing
sf_use_s2(FALSE)  # Disable S2 spherical geometry
cores <- parallel::detectCores() - 1

cat("Creating line segment buffers...\n")
const_segment_buffers <- create_buffers_in_batches(df.const.lines, buffer_dist = 1000, batch_size = 250)

# Return to sequential processing
future::plan(future::sequential)
sf_use_s2(TRUE)  # Re-enable S2 spherical geometry

# Find accidents near construction segments
accidents_near_construction <- df.acc.sf %>%
  st_join(const_segment_buffers, join = st_intersects)

>>>>

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

@@

```{r Packages}
library(data.table)   # For faster data manipulation
library(tidyverse)    # For data manipulation and visualization
library(sf)           # For spatial data handling
library(leaflet)      # For interactive maps
library(leaflet.extras) # For additional leaflet features
library(mapview)      # For easier map visualization
library(tmap)         # For thematic maps
library(tigris)       # For US road networks
library(future)       # For parallel processing
library(future.apply) # For parallel processing with apply functions
library(sf)           # For spatial data handling
library(RPostgres)    # For PostgreSQL connection
library(DBI)          # For database interface

@@

```{r Data Load Roads}
# Get US roads (this can be slow for the entire US, so we might want to limit by state)
# We also only get Primary and Secondary roads as they are the most important (i.e., where most constructions and accidents happen). Otherwise, the dataset would become to large (1.1GB)

ca_roads <- primary_secondary_roads("CA", year = 2021)

# Below code to get ALL roads for California (not recommended due to size)

# First get all counties in California
#ca_counties <- counties("CA", year = 2021)

# Then get roads for each county
#ca_roads_list <- lapply(ca_counties$COUNTYFP, function(county_code) {
#  roads("CA", county = county_code, year = 2021)
#})

# Optionally combine all county road data into one object
#ca_roads <- do.call(rbind, ca_roads_list)
```

```{r Static Maps}
# Static map for Accidents with year coloring
# First, store your plot in a variable
ca_plot <- ggplot() +
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  geom_sf(data = df.acc.sf %>% filter(State == "CA"), 
          aes(color = factor(year)), alpha = 0.7, size = 0.5) +
  scale_color_viridis_d(name = "Year") +  # Use viridis color palette for discrete values
  theme_minimal() +
  labs(title = "US Road Accidents by Year (2016-2021)") +
  theme(legend.position = "bottom")
print(ca_plot)
# Then save it using ggsave
ggsave(filename = "imgs/california_accidents.png", 
       plot = ca_plot,
       width = 10, # width in inches
       height = 8, # height in inches
       dpi = 300)  # resolution

# Construction sites map with year coloring
# First, store our plot in a variable
ca_const_plot <- ggplot() +
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  geom_sf(data = df.const.sf %>% filter(State == "CA"), 
          aes(color = factor(year)), alpha = 0.7, size = 0.5) +
  scale_color_viridis_d(name = "Year") +  # Use viridis color palette for discrete values
  theme_minimal() +
  labs(title = "US Construction Sites by Year (2016-2021)") +
  theme(legend.position = "bottom")
print(ca_const_plot)
# Then save it using ggsave
ggsave(filename = "imgs/california_construction.png", 
       plot = ca_const_plot,
       width = 10, # width in inches
       height = 8, # height in inches
       dpi = 300)  # resolution
```

```{r Heatmap static}
# Create heatmap of accidents using ggplot2
accident_heatmap <- ggplot() +
  # Add California roads as base layer
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  # Create density heatmap
  stat_density_2d(
    data = df.acc %>% filter(!is.na(Start_Lat) & !is.na(Start_Lng)),
    aes(x = Start_Lng, y = Start_Lat, fill = after_stat(density)),
    geom = "tile", 
    contour = FALSE,
    alpha = 0.7,
    h = 0.1,  # Bandwidth - adjust to match leaflet radius
    n = 200   # Resolution - higher values create smoother heatmap
  ) +
  # Use color scheme similar to leaflet's default heatmap
  scale_fill_gradientn(
    colors = c("#0000FF", "#00FFFF", "#00FF00", "#FFFF00", "#FF0000"),
    name = "Accident\nDensity"
  ) +
  # Set appropriate boundaries for California
  coord_sf(
    xlim = c(-124.5, -114.5),
    ylim = c(32.5, 42.5)
  ) +
  theme_minimal() +
  labs(
    title = "Accident Density Heatmap in California (2016-2021)",
    x = NULL,
    y = NULL
  ) +
  theme(
    legend.position = "right",
    plot.title = element_text(face = "bold")
  )
# Display the plot
print(accident_heatmap)
```

```{r Construction Heatmap static}
# Create heatmap of construction sites using ggplot2
construction_heatmap <- ggplot() +
  # Add California roads as base layer
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  # Create density heatmap
  stat_density_2d(
    data = df.const %>% filter(!is.na(Start_Lat) & !is.na(Start_Lng)),
    aes(x = Start_Lng, y = Start_Lat, fill = after_stat(density)),
    geom = "tile", 
    contour = FALSE,
    alpha = 0.7,
    h = 0.1,  # Bandwidth
    n = 200   # Resolution
  ) +
  # Use color scheme matching your leaflet construction map
  scale_fill_gradientn(
    colors = c("yellow", "orange", "red"),
    name = "Construction\nDensity"
  ) +
  # Set appropriate boundaries for California
  coord_sf(
    xlim = c(-124.5, -114.5),
    ylim = c(32.5, 42.5)
  ) +
  theme_minimal() +
  labs(
    title = "Construction Density Heatmap in California (2016-2021)",
    x = NULL,
    y = NULL
  ) +
  theme(
    legend.position = "right",
    plot.title = element_text(face = "bold")
  )
# Display the plot
print(construction_heatmap)
```

@@

We construct construction sites now also as line objects since they have a start and end point

```{r Construction linestrings}
# Convert construction data to linestring sf object
df.const.lines <- df.const %>%
  filter(!is.na(Start_Lat) & !is.na(Start_Lng) & !is.na(End_Lat) & !is.na(End_Lng)) %>%
  mutate(geometry = pmap(list(Start_Lng, Start_Lat, End_Lng, End_Lat), 
                         function(start_lng, start_lat, end_lng, end_lat) {
                           coords <- matrix(c(start_lng, start_lat, 
                                             end_lng, end_lat), 
                                           ncol = 2, byrow = TRUE)
                           st_linestring(coords)
                         })) %>%
  st_sf(crs = 4326)
```

## Spatial operations in PostgreSQL

Since file sizes are so large and Spatial operations in R incredibly slow, we retreat to a PostgreSQL database for the following operations (PostGIS also uses the SF framework, thus R are almost identical to the following SQL functions used).

```{r DB ops}
# Create a connection to your PostgreSQL database
con <- dbConnect(
  Postgres(),
  dbname = "geospatial_final",
  host = "localhost",
  port = 5432,
  # Uncomment and add your credentials if needed
  user = "postgres",
  password = Sys.getenv("POSTGRES_PWD")
)

# Set connection parameters for performance optimization
dbExecute(con, "SET work_mem = '128MB'")           # Increase working memory
dbExecute(con, "SET maintenance_work_mem = '256MB'") # For index creation
dbExecute(con, "SET random_page_cost = 1.1")       # For SSD storage
dbExecute(con, "SET effective_cache_size = '2GB'") # Estimate of memory available
dbExecute(con, "SET max_parallel_workers_per_gather = 4") # Use multiple cores

# Check if PostGIS extension is enabled
postgis_check <- dbGetQuery(con, "SELECT PostGIS_version()")
cat("PostGIS version:", postgis_check[[1]], "\n")

# Check if SRID 3310 is available and add if not
dbExecute(con, "
  DO $$
  BEGIN
    IF NOT EXISTS (SELECT 1 FROM spatial_ref_sys WHERE srid = 3310) THEN
      INSERT INTO spatial_ref_sys (srid, auth_name, auth_srid, proj4text, srtext)
      VALUES (3310, 'EPSG', 3310, 
      '+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +datum=NAD83 +units=m +no_defs',
      'PROJCS[\"NAD83 / California Albers\",GEOGCS[\"NAD83\",DATUM[\"North_American_Datum_1983\",SPHEROID[\"GRS 1980\",6378137,298.257222101,AUTHORITY[\"EPSG\",\"7019\"]],AUTHORITY[\"EPSG\",\"6269\"]],PRIMEM[\"Greenwich\",0,AUTHORITY[\"EPSG\",\"8901\"]],UNIT[\"degree\",0.01745329251994328,AUTHORITY[\"EPSG\",\"9122\"]],AUTHORITY[\"EPSG\",\"4269\"]],PROJECTION[\"Albers_Conic_Equal_Area\"],PARAMETER[\"standard_parallel_1\",34],PARAMETER[\"standard_parallel_2\",40.5],PARAMETER[\"latitude_of_center\",0],PARAMETER[\"longitude_of_center\",-120],PARAMETER[\"false_easting\",0],PARAMETER[\"false_northing\",-4000000],UNIT[\"metre\",1,AUTHORITY[\"EPSG\",\"9001\"]],AUTHORITY[\"EPSG\",\"3310\"]]');
    END IF;
  END
  $$;
")

# Check if tables exist and only create them if they don't
# Begin transaction for data processing
dbExecute(con, "BEGIN")

# Check if accidents table exists, if not create it
has_accidents <- dbGetQuery(con, "SELECT EXISTS (SELECT 1 FROM information_schema.tables WHERE table_schema = 'public' AND table_name = 'accidents')")$exists
if (!has_accidents) {
  # Write accidents data to database
  sf::st_write(df.acc.sf, con, "accidents", 
               layer_options = c("GEOM_TYPE=GEOMETRY", 
                                 "GEOMETRY_NAME=geometry",
                                 "SRID=4326"))
  cat("Written accidents data to database\n")

  # Create spatial index for accidents
  dbExecute(con, "CREATE INDEX idx_accidents_geometry ON accidents USING GIST(geometry)")
  dbExecute(con, "ANALYZE accidents")
  cat("Created spatial index for accidents table\n")
}

# Check if construction table exists, if not create it
has_construction <- dbGetQuery(con, "SELECT EXISTS (SELECT 1 FROM information_schema.tables WHERE table_schema = 'public' AND table_name = 'construction')")$exists
if (!has_construction) {
  # Write construction data to database
  sf::st_write(df.const.sf, con, "construction", 
               layer_options = c("GEOM_TYPE=GEOMETRY", 
                                 "GEOMETRY_NAME=geometry",
                                 "SRID=4326"))
  cat("Written construction data to database\n")

  # Create spatial index for construction
  dbExecute(con, "CREATE INDEX idx_construction_geometry ON construction USING GIST(geometry)")
  dbExecute(con, "ANALYZE construction")
  cat("Created spatial index for construction table\n")
}

# Check if construction table with lines exists, if not create it
has_construction_lines <- dbGetQuery(con, "SELECT EXISTS (SELECT 1 FROM information_schema.tables WHERE table_schema = 'public' AND table_name = 'construction_lines')")$exists
if (!has_construction_lines) {
  # Write construction data to database
  sf::st_write(df.const.lines, con, "construction_lines", 
               layer_options = c("GEOM_TYPE=GEOMETRY", 
                                 "GEOMETRY_NAME=geometry",
                                 "SRID=4326"))
  cat("Written construction_lines data to database\n")

  # Create spatial index for construction
  dbExecute(con, "CREATE INDEX idx_construction_lines_geometry ON construction_lines USING GIST(geometry)")
  dbExecute(con, "ANALYZE construction_lines")
  cat("Created spatial index for construction_lines table\n")
}

# Commit transaction for base tables
dbExecute(con, "COMMIT")

# Begin transaction for buffer creation
dbExecute(con, "BEGIN")

# Check if construction_buffers table exists, if not create it
has_construction_buffers <- dbGetQuery(con, "SELECT EXISTS (SELECT 1 FROM information_schema.tables WHERE table_schema = 'public' AND table_name = 'construction_buffers')")$exists
if (!has_construction_buffers) {
  # Create construction buffers table
  dbExecute(con, "
    CREATE TABLE construction_buffers AS
    SELECT 
      \"ID\" as id,
      ST_Transform(
        ST_Buffer(
          ST_Transform(geometry, 3310), 
          300
        ), 
        4326
      ) AS geometry
    FROM construction
  ")

  # Add primary key and spatial index
  dbExecute(con, "ALTER TABLE construction_buffers ADD PRIMARY KEY (id)")
  dbExecute(con, "CREATE INDEX idx_construction_buffers_geometry ON construction_buffers USING GIST(geometry)")
  dbExecute(con, "SELECT UpdateGeometrySRID('construction_buffers', 'geometry', 4326)")
  dbExecute(con, "ANALYZE construction_buffers")
  cat("Created construction_buffers table with spatial index\n")
}

# Commit buffer transaction
dbExecute(con, "COMMIT")

# Begin transaction for join table
dbExecute(con, "BEGIN")

# Check if accidents_in_construction table exists, if not create it
has_accidents_in_construction <- dbGetQuery(con, "SELECT EXISTS (SELECT 1 FROM information_schema.tables WHERE table_schema = 'public' AND table_name = 'accidents_in_construction')")$exists
# Check if accidents_in_construction table exists, if not create it
has_accidents_in_construction <- dbGetQuery(con, "SELECT EXISTS (SELECT 1 FROM information_schema.tables WHERE table_schema = 'public' AND table_name = 'accidents_in_construction')")$exists
if (!has_accidents_in_construction) {
  # Create join table with spatial and temporal constraints
  dbExecute(con, "
    CREATE TABLE accidents_in_construction AS
    SELECT 
      a.\"ID\" AS accident_id,
      b.id AS construction_id
    FROM 
      accidents a
    JOIN 
      construction_buffers b ON ST_Within(a.geometry, b.geometry)
    JOIN 
      construction c ON b.id = c.\"ID\"
    WHERE
      -- Join only when accident date overlaps with construction date period
      (a.\"Start_Time\" BETWEEN c.\"Start_Time\" AND c.\"End_Time\")
      OR 
      (a.\"End_Time\" BETWEEN c.\"Start_Time\" AND c.\"End_Time\")
      OR 
      (a.\"Start_Time\" <= c.\"Start_Time\" AND a.\"End_Time\" >= c.\"End_Time\")
  ")

  # Add primary key and indices
  dbExecute(con, "ALTER TABLE accidents_in_construction ADD PRIMARY KEY (accident_id, construction_id)")
  dbExecute(con, "CREATE INDEX idx_aic_accident_id ON accidents_in_construction(accident_id)")
  dbExecute(con, "CREATE INDEX idx_aic_construction_id ON accidents_in_construction(construction_id)")
  dbExecute(con, "ANALYZE accidents_in_construction")
  cat("Created accidents_in_construction table with indices\n")
}

# Commit join transaction
dbExecute(con, "COMMIT")

# Read the joined data back into R
accidents_with_construction <- st_read(con, query = "
  SELECT 
    a.*, 
    c.\"ID\" AS construction_id
  FROM 
    accidents a
  LEFT JOIN 
    accidents_in_construction b ON a.\"ID\" = b.accident_id
  LEFT JOIN 
    construction c ON b.construction_id = c.\"ID\"
")

accidents_per_zone <- st_read(con, query = "
  SELECT 
    c.\"ID\" AS construction_id,
    COUNT (*) AS accident_count,
    c.geometry
  FROM 
    accidents a
  LEFT JOIN 
    accidents_in_construction b ON a.\"ID\" = b.accident_id
  LEFT JOIN 
    construction c ON b.construction_id = c.\"ID\"
  GROUP BY c.\"ID\", c.geometry
")

# Disconnect from database
dbDisconnect(con)

# Example of additional analysis with the joined data
cat("Total accidents:", nrow(accidents_with_construction), "\n")
cat("Accidents within construction areas:", sum(!is.na(accidents_with_construction$construction_id)), "\n")
```

@@

In theory, the commented code below would achieve the same as our operation PostGIS but way slower. We will not run it here, but keep it to demonstrate that we could implement in R as well.

```{r Buffer Zone Analysis}
# Set up parallel processing
#future::plan(future::multisession, workers = parallel::detectCores() - 1)

# Set sf to use parallel processing
#sf_use_s2(FALSE)  # Disable S2 spherical geometry
#cores <- parallel::detectCores() - 1

# Process each dataset with batching
#cat("Creating point buffers...\n")
#const_buffers <- create_buffers_in_batches(df.const.sf, buffer_dist = 1000, batch_size = 500)

# Compute accidents within construction zones
#accidents_in_construction <- df.acc.sf %>%
#  st_join(const_buffers, join = st_within, prepared = TRUE)

# Return to sequential processing
#future::plan(future::sequential)
#sf_use_s2(TRUE)  # Re-enable S2 spherical geometry

# Count accidents per construction zone
#accidents_per_zone <- accidents_with_construction %>%
#  group_by(ID) %>%  # Grouping by the ID column
#  summarize(accident_count = n())

accidents_per_zone <- accidents_per_zone %>% drop_na()

# Visualize construction zones with accident counts
# First, store our plot in a variable
accident_zones_plot <- ggplot() +
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  geom_sf(data = accidents_per_zone %>% arrange(accident_count), 
          aes(color = accident_count), size = 1.5) +
  scale_color_viridis_c() +
  theme_minimal() +
  labs(title = "Accident Counts within Construction Zones (2016-2021)")

@@

# Then save it using ggsave
ggsave(filename = "imgs/accident_counts_construction_zones.png", 
       plot = accident_zones_plot,
       width = 10, # width in inches
       height = 8, # height in inches
       dpi = 300)  # resolution
```

## Advanced construction sit analysis (line objects):

```{r Maps with Construction Lines - static}
# Static map with construction line segments
ggplot() +
  geom_sf(data = ca_roads, color = "gray80", size = 0.1) +
  geom_sf(data = df.const.lines %>% filter(State == "CA"), 
          color = "orange", size = 1) +
  theme_minimal() +
  labs(title = "US Construction Segments (2016-2021)")
```

```{r Maps with Construction Lines - dynamic}
# Interactive map with construction segments focused on California
construction_segment_map <- leaflet() %>%
  addTiles() %>%
  addPolylines(data = df.const.lines, 
               color = "orange",
               weight = 3,
               opacity = 0.7,
               popup = ~paste("ID:", ID, "<br>Duration:", duration)) %>%
  setView(lng = -119.4179, lat = 36.7783, zoom = 6) %>%  # Center on California
  setMaxBounds(lng1 = -124.6, lat1 = 42.0,    # Northwest corner of CA
               lng2 = -114.1, lat2 = 32.5)    # Southeast corner of CA

@@

Again, we execute computationally heavy operations in PostGIS but have the commented R code below to showcase a theoretical, but slow implementatiojn in R.

```{r Construction Impact Analysis with Buffers}
# Set up parallel processing
#future::plan(future::multisession, workers = parallel::detectCores() - 1)

# Set sf to use parallel processing
#f_use_s2(FALSE)  # Disable S2 spherical geometry
#cores <- parallel::detectCores() - 1

#cat("Creating line segment buffers...\n")
#const_segment_buffers <- create_buffers_in_batches(df.const.lines, buffer_dist = 1000, batch_size = 250)

# Find accidents near construction segments
#accidents_near_construction <- df.acc.sf %>%
#  st_join(const_segment_buffers, join = st_intersects, prepared = TRUE)

# Return to sequential processing
#future::plan(future::sequential)
#sf_use_s2(TRUE)  # Re-enable S2 spherical geometry
